Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/experiments.tex
Paper update

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB algorithm, the local penalization
method with EI acquisition function (EI-LP), the qEI and qKG
methods\footnote{We implemented the BLCB algorithm as the available open source
implementations only allow discrete input. For the EI-LP method, the code is
downloaded from https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG
is downloaded from https://github.com/wujian16/Cornell-MOE}. 
% For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
% used and the GP models are fitted by maximum likelihood estimations(MLE); for
% the qKG and qEI methods, the Matern52 kernel is used, and the GP
% hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
% integration are the default strategies of the qKG and qEI implementations and
% it is unclear in the documentation about how to change the GP settings.

@@

@@

\begin{figure}[h]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
        \caption{Schematic of the operational amplifier}
        \label{fig:schDAC2014}
    \end{center}
    \vskip -0.2in
\end{figure}

\begin{figure}[]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{fig:resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}

@@

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batch
mode. For the batch runs, the MACE converges fastest among the three
algorithms, while the sequential MACE (MACE-1) has comparable performance as
the batch EI-LP (EI-LP-4) method.

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB
algorithm~\cite{desautels2014parallelizing}, the local penalization method with
EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
methods~\cite{qEI,wu2016parallel}\footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE}.

For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
used and the GP models are fitted by maximum likelihood estimations(MLE); for
the qKG and qEI methods, the ARD Matern52 kernels are used, and the GP
hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
integration are the default strategies of the qKG and qEI implementations and
it is unclear in the documentation about how to change the GP settings.

@@

\begin{figure}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
        \caption{Schematic of the operational amplifier}
        \label{fig:schDAC2014}
    \end{center}
    \vskip -0.2in
\end{figure}

@@

\begin{figure}[!htb]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{fig:resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
    \vskip -0.15in
\end{figure}

@@

The optimization results of the class-E power amplifier are given in
Figure~\ref{fig:resClassE} and Table~\ref{tab:result_PA}. We can see that the
MACE outperformed the BLCB and EI-LP in both sequential and batch mode. For the
batch runs, the MACE converges fastest among the three algorithms, while the
sequential MACE (MACE-1) has comparable performance as the batch EI-LP
(EI-LP-4) method.
